The Astropy Project

### 2017-11-11 main.tex
not specialized

\section{Introduction} \label{sec:intro}
% first draft by Moritz (hamogu)
% heavily edited by Adrian PW - let me know if you want to revert anything!
All astronomical research makes use of software in some way.
Astronomy as a field has thus long supported the development of specialized
software tools for astronomical tasks, from software packages that enable
individualized scientific research to data reduction tools and pipelines that
enable collaborations and survey operations.
Some such software packages are or were supported by large institutions and are
intended for a wide range of users.
These packages typically provide some level of documentation and user support or
training.
Other packages are developed by individual researchers or research groups and
are then typically used by smaller groups for more domain-specific purposes.
Whether for a package meant for wide distribution or for scripts and programs
for a specific research project, the implementation of astronomical software can
be eased through the use of a library that provides core functionality that is
common to many astronomical tasks.
The users of such software then also benefit from a community and ecosystem
built around a common foundation.
The \astropy project has grown to become this community, and the \astropypkg
core package a feature-rich library for \python-based astronomical software.

>>>>

\section{Introduction} \label{sec:intro}
% first draft by Moritz (hamogu)
% heavily edited by Adrian PW - let me know if you want to revert anything!
All astronomical research makes use of software in some way.
Astronomy as a field has thus long supported the development of software tools
for astronomical tasks, from software packages that enable individualized
scientific research to data reduction tools and pipelines that enable
collaborations and survey operations.
Some such software packages are or were supported by large institutions and are
intended for a wide range of users.
These packages typically provide some level of documentation and user support or
training.
Other packages are developed by individual researchers or research groups and
are then typically used by smaller groups for more domain-specific purposes.
Whether for a package meant for wide distribution or for scripts and programs
for a specific research project, the implementation of astronomical software can
be eased through the use of a library that provides core functionality that is
common to many astronomical tasks.
The users of such software then also benefit from a community and ecosystem
built around a common foundation.
The \astropy project has grown to become this community, and the \astropypkg
core package a feature-rich library for \python-based astronomical software.
